A pipeline to analyse time-course gene expression data

### 2020-07-17 scripts/manuscript.Rmd
fix errors in heatmap

# order the observations by Group, then time, then replicate
orderedMeta<-colData(moanin_model)
ord = order(
  orderedMeta$Group,
  orderedMeta$Timepoint,
  orderedMeta$Replicate)
orderedMeta$Timepoint = as.factor(orderedMeta$Timepoint)

@@

res = aheatmap(
    assay(moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=orderedMeta[,
                c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)

>>>>

# order the observations by Group, then time, then replicate
orderedMeta<-data.frame(colData(moanin_model))
ord = order(
  orderedMeta$Group,
  orderedMeta$Timepoint,
  orderedMeta$Replicate)
orderedMeta$Timepoint = as.factor(orderedMeta$Timepoint)

@@

res = aheatmap(
    assay(moanin_model[genes_to_plot,ord]),
    Colv=NA,
    color="YlGnBu",
    annCol=orderedMeta[,c("Group", "Timepoint")],
    annLegend=FALSE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(raw)"),
    treeheight=0, legend=FALSE)
